Robotic Manipulator Path Planning Utilizing Interpolated 3D Voxel-Based Obstacle Avoidance Method

### 2023-11-15 Articles/Article 1/main.tex
minor

\add{
	- what is the point of this part anyways \\
	- but how do we limit this - this chapter only makes sense if we describe how the limits are applied
}

>>>>

\add{
	- what is the point of this part anyways \\
	- YES, BUT HOW DO WE APPLY THOSE - this chapter only makes sense if we describe how the limits are applied
}
